---
title: "Full tutorial"
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(tidyverse.quiet = TRUE)
```

# Importing the data

In this section we will use the data in the ex_data folder.
More ressources on data import are available in [this vignette](https://plant-functional-trait-course.github.io/fluxible/articles/data-prep.html) on the fluxible website.


## Importing log file

Importing the log and turning it into a dataframe with chamber ID (port nb), chamber closing time and re-opening time.
```{r}
#| label: "import-log"

library(tidyverse)

# building col names
chamber_colnames <- c(
    "port", "valvestatus", "chamberstatus",
    "aux1", "aux2", "aux3", "aux4", "aux5",
    "temperaturev", "pressurev"
    )
log_colnames <- c(
    "epochtime",
    rep(chamber_colnames, times = 12)
)

chamber_log_read <- read_log("ex_log/FRMonitor_0012.log", col_names = log_colnames)
# repeated colnames are normal
chamber_log <- chamber_log_read |>
    pivot_longer(!c(epochtime), names_to = c(".value", "variable"), names_sep = "_") |>
    filter(
        port %in% c(1:12) # we filter out all the rows with port -1
        & chamberstatus %in% c(1:3) # very conservative, we can adjust the focus window later in flux_fitting
    ) |>
    arrange(epochtime) |> # just to be sure
    mutate( # without grouping
        measurement_id = consecutive_id(port),
        datetime = as_datetime(epochtime) # we work in datetime
    ) |>
    mutate(
        .by = c(measurement_id),
        closing = min(datetime),
        opening = max(datetime)
    ) |>
    select(measurement_id, port, closing, opening) |>
    distinct()
View(chamber_log)
```

Possible improvements

- take into account the chamber status better and  use it to by-pass the start and end cuts in flux_fitting. Opening and closing status would be "cut" (not used for fitting but visible on the plot), and fully open would be "keep".
- keep the other columns
- read several log files
- need temperature and pressure for flux calculation

## Importing data file

```{r}
#| label: "import-data"

data_read <- read_table("ex_data/JFAADS2294-20241211-193921-DataLog_User.dat")

data <- data_read |>
    mutate(
        f_datetime = as_datetime(paste(DATE, TIME))
    ) |>
    select(f_datetime, CO2_dry) # we keep it simple for now and work only on CO2

View(data)
```

Improvements

- read several files

# Processing the data

```{r}
#| label: "fluxible-match"

library(fluxible)

conc <- flux_match(
    raw_conc = data,
    field_record = chamber_log,
    f_datetime = f_datetime,
    start_col = closing,
    end_col = opening,
    fixed_length = FALSE
) |>
    drop_na(CO2_dry)

```

```{r}
#| label: "fluxible-fitting"

conc_fit <- flux_fitting(
    conc_df = conc,
    f_conc = CO2_dry,
    fit_type = "exp_zhao18"
)

```

```{r}
#| label: "fluxible-quality"

conc_flags <- flux_quality(
    slopes_df = conc_fit,
    f_conc = CO2_dry
)

```

```{r}
#| label: "fluxible-plot"

flux_plot(
    conc_flags,
    f_conc = CO2_dry)

```
