---
title: "Full tutorial"
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(tidyverse.quiet = TRUE)
```

# Importing the data

In this section we will use the data in the ex_data folder.
More ressources on data import are available in [this vignette](https://plant-functional-trait-course.github.io/fluxible/articles/data-prep.html) on the fluxible website.


## Importing log file

Importing the log and turning it into a dataframe with chamber ID (port nb), chamber closing time and re-opening time.
```{r}
#| label: "import-log"
#| warning: false
#| message: false

library(tidyverse)

# building col names
chamber_colnames <- c(
    "port", "valvestatus", "chamberstatus",
    "aux1", "aux2", "aux3", "aux4", "aux5",
    "temperaturev", "pressure"
    )
log_colnames <- c(
    "epochtime",
    rep(chamber_colnames, times = 12)
)

chamber_log_read <- list.files(
    "ex_log",
    full.names = TRUE
) |>
    map_dfr(
        read_log,
        col_names = log_colnames
    )
# read_log("ex_log/FRMonitor_0012.log", col_names = log_colnames)
# repeated colnames are normal
chamber_log_all <- chamber_log_read |>
    pivot_longer(!c(epochtime), names_to = c(".value", "variable"), names_sep = "_") |>
    filter(
        port %in% c(1:12) # we filter out all the rows with port -1
    ) |>
    arrange(epochtime) |> # just to be sure
    mutate( # without grouping
        chamber = case_when(
            chamberstatus %in% c(1:3) ~ "open",
            chamberstatus == 0 ~ "closed"
        ),
        change_id = consecutive_id(port, chamberstatus), #detecting if same port but new measurement
        datetime = as_datetime(epochtime) # we work in datetime
    ) |>
    filter(
        # chamberstatus %in% c(1:3) # very conservative, we can adjust the focus window later in flux_fitting
        chamberstatus == 1
        # valvestatus == 10
    ) |>
    mutate(
        measurement_id = consecutive_id(change_id) # just getting rid of the missing id after filter
        )
    
chamber_log <- chamber_log_all |>
    mutate(
        .by = c(measurement_id),
        closing = min(datetime) - 300, # can be recut in flux_fitting, but so we see better
        opening = max(datetime) + 300
    ) |>
    select(measurement_id, port, closing, opening) |>
    distinct()

# We make a separate df for temp and pressure so we keep the 4 seconds reads
chamber_temp_pres <- chamber_log_all |>
    mutate(
        air_temp = temperaturev * 15, # need to ask the exact conversion factor, for now this one makes sense
        pressure = pressure / 101.325 # need atm for fluxible
    ) |>
    select(datetime, air_temp, pressure)

# View(chamber_log_all)
```

Possible improvements

- take into account the chamber status better and  use it to by-pass the start and end cuts in flux_fitting. Opening and closing status would be "cut" (not used for fitting but visible on the plot), and fully open would be "keep".
- keep the other columns
- Because of the inconsistant offset between the closing of the chamber and the start of the flux, it is difficult to make a proper record of start/end of fluxes.

## Importing data file

```{r}
#| label: "import-data"
#| warning: false
#| message: false

data_read <- list.files(
    "ex_data",
    full.names = TRUE
) |>
    map_dfr(
        read_table
    )
# read_table("ex_data/JFAADS2294-20241211-193921-DataLog_User.dat")

data <- data_read |>
    mutate(
        f_datetime = as_datetime(paste(DATE, TIME))
    ) |>
    left_join(chamber_temp_pres, by = join_by(f_datetime == datetime)) |> # adding air temp and pressure here
    select(f_datetime, CO2_dry, air_temp, pressure) # we keep it simple for now and work only on CO2

# View(data)
```

```{r}
#| label: fig-fluxes
#| echo: false
#| eval: false
#| message: FALSE
#| warning: false
#| fig-width: 10
#| fig-height: 8
#| fig-cap: "Exploring where the fluxes are, because there is an offset in time."

library(ggplot2)

data |>
    filter(
        f_datetime <= ymd_hms("2024-12-11 21:00:00")
    ) |>
    ggplot(aes(f_datetime, CO2_dry)) +
    theme_bw() +
    geom_point() +
    scale_x_datetime(date_breaks = "30 min",
        minor_breaks = "5 min",
        date_label = "%e/%m \n %H:%M")

```

# Processing the data

```{r}
#| label: "fluxible-match"

library(fluxible)

conc <- flux_match(
    raw_conc = data,
    field_record = chamber_log,
    f_datetime = f_datetime,
    start_col = closing,
    end_col = opening,
    fixed_length = FALSE,
    time_diff = -15000 # 4h10
) |>
    drop_na(CO2_dry)
# View(conc)
```

```{r}
#| label: "fluxible-fitting"

conc_fit <- flux_fitting(
    conc_df = conc,
    f_conc = CO2_dry,
    fit_type = "linear",
    # fit_type = "exp_zhao18",
    start_cut = 300,
    end_cut = 300
)
# View(conc_fit)
```

```{r}
#| label: "fluxible-quality"

conc_flags <- flux_quality(
    slopes_df = conc_fit,
    f_conc = CO2_dry,
    force_discard = 72 # obviously a complete mismatch
)
# View(conc_flags)
```

```{r}
#| label: "fluxible-plot"
#| eval: false

flux_plot(
    conc_flags,
    f_conc = CO2_dry,
    print_plot = FALSE,
    output = "pdfpages",
    scale_x_datetime_args = list(
        date_breaks = "10 min",
        minor_breaks = "2 min",
        date_label = "%e/%m \n %H:%M"
    ),
    f_plotname = "eosense4h10f",
    f_ylim_upper = 650
    )

```

Note: I found a bug in flux_calc, it is not dealing well with the pressure as a variable.
It is fixed in fluxible v1.2.5 (dev version), if you are using the CRAN version (v1.2.2) you will need to set the pressure as a constant.
```{r}
#| label: "fluxible-calc"

fluxible_df <- flux_calc(
    slopes_df = conc_flags,
    slope_col = f_slope_corr,
    temp_air_col = air_temp,
    setup_volume = 72, # not sure if correct, found on website
    # setup_volume = 4.756,
    plot_area = 0.21, # to check
    # plot_area = 0.032,
    # atm_pressure = 1,
    atm_pressure = pressure,
    conc_unit = "ppm",
    flux_unit = "umol/m2/s",
    cols_keep = "f_quality_flag"
) |>
    rename(
        fluxible_flux = "f_flux",
        fluxible_slope = "f_slope_corr"
    ) |>
    mutate(
        f_datetime = f_datetime + 29329 # correcting the other way to match eosense
    )
# View(fluxible_df)

saveRDS(fluxible_df, "compare_data/fluxible_df.rds")
```

Structure of fluxible_df:
```{r}
#| label: fluxes-str
#| echo: false

str(fluxible_df, width = 70, strict.width = "cut")

```
